Article Title

### 2013-12-16 plos.tex
outline of discussion

It is therefore important to compare multiple families of regularized estimators on the system under investigation. The family that consistently outperforms the others may be proposed as candidate low-dimensional representation of the correlation structure. The greater efficiency of one estimator over another is not a mathematical necessity but an empirical finding depending on the prevalent types of correlation structure in the investigated system.

In this study, we compared four families of regularized combining partial interactions and latent units: `shrinkage toward diagonal', `shrinkage toward a multifactor model', `sparse partial correlations', and 'sparse+latent partial correlations'.  First, in simulation with known low-dimensional structure of correlations, we demonstrate that regularized estimators from matching families of low-dimensional targets generally outperform all other estimators. We then repeat this study on neural data from dense groups of neurons in mouse visual cortex under visual stimulation. We find that most efficient estimation was achieved by modeling correlations as a sparse network of partial correlations combined with several latent units interacting with the entire population. Finally, we analyze the relationship between the elements of such estimates and other properties of the circuit such as physical distances between neurons and their preferred orientations.

@@

\section*{Discussion}
\subsection*{Functional connectivity from big neural data}
Breakthroughs in neuroscience

>>>>

\subsection*{Model selection}
Covariance selection is but one of numerous possible low-dimensional approximations of the covariance matrix. Indeed any probabilistic model of the joint population activity regularized toward a small number of parameters automatically defines a low-dimensional approximation of the covariance matrix. Models that accurately reflect the dominant functional dependencies in the circuit, its so-called ``functional connectivity'', will tend to produce estimates that are nearest to the true value of the covariance matrix and are said to be more \emph{efficient} or to \emph{dominate} other estimators. An estimator's superior efficiency can be ascertained by cross-validation.  Because different types of neural circuits are governed by different types of dependencies, different probabilistic models and covariance matrix estimators may dominate in each case. The estimator that is shown to dominate all others for a specific type of neural circuit may be proposed as the best descriptor of the low-dimensional representation of the correlation structure of the system of interest. Its structure may then be analyzed and related to the circuits anatomical organization.

\subsection*{Summary of findings}
In this study, we compared four regularized covariance matrix estimators biased toward different respective low-dimensional correlation structures: `shrinkage toward diagonal' or $C_{\sf diag}$, `shrinkage toward a multifactor model' or $C_{\sf factor}$, `sparse partial correlations' or $C_{\sf sparse}$, and 'sparse partial correlations with latent units' or $C_{\sf sparse+lowrank}$.  First, we demonstrated that, in simulations with known true low-dimensional correlation structures, regularized estimators with matching types of low-dimensional structure generally dominated over the other estimators. We then used cross-validation to determine the most efficient estimator for the population activity of dense groups of neurons in mouse primary visual cortex. We found that $C_{\sf sparse+lowrank}$ consistently dominated the other estimators.  Estimate produced by $C_{\sf sparse+lowrank}$ revealed networks of interactions that differed substantially from networks of strongest correlations and depended strongly on the physical distance separating pairs of cells and on the differences in their preferred orientations.

@@

\section*{Discussion}
\subsection*{Functional connectivity from big neural data}
Transformational breakthroughs in neuroscience are anticipated to emerge from technological developments that will allow simultaneous recordings of the spiking activity of much larger subsets of neurons in functioning neural circuits than have been possible thus far.
